Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-02-18 Grassmannian_cells.tex
Minor edit

\begin{theorem}\label{celldec}The following holds:
\begin{enumerate}
\item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq m-1$. Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
\end{enumerate}
\end{theorem}
\begin{proof}
The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover}. The dual version for preinjective representations follows as $\Gr_{\tbfe}(P_m)\cong\Gr_{\udim P_m-\tbfe}(I_m)$.

>>>>

\begin{theorem}\label{celldec}The following holds:
\begin{enumerate}
\item Every quiver Grassmannian of any indecomposable preprojective or preinjective representation of $K(n)$ and $\widetilde{K(n)}$ has a cell decomposition into affine spaces.
\item Let $X$ be an indecomposable representation of dimension $(d,e)$ or $(e,d)$ where $(d,e)=\udim P_m-r\udim P_{m-1}$ for $m\geq 2$ and $\leq 0\leq r\leq n-1$. Then every quiver Grassmannian $\Gr_{\bfe}(X)$ has a cell decomposition into affine spaces.
\end{enumerate}
\end{theorem}
\begin{proof}
The first part follows by combining the results of Section \ref{torusaction} and Theorems \ref{thm:bb} and \ref{cellscover}. The dual version for preinjective representations follows as $\Gr_{\tbfe}(P_m)\cong\Gr_{\udim P_m-\tbfe}(I_m)$.
